Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-09-08 Papers/ms.tex
referee

\section*{Acknowledgements}
It is a pleasure to thank Phil Marshall (Stanford), Tommaso Treu (UCLA),
Ross Fadely (NYU), and Alan Heavens (Edinburgh)
for valuable discussion. Thomas Lumley (Auckland) also deserves credit for
ending BJB's usage of the jet colormap.
This work was funded by a Marsden Fast Start grant from the Royal Society of
New Zealand.

>>>>

\section*{Acknowledgements}
It is a pleasure to thank Phil Marshall (Stanford), Tommaso Treu (UCLA),
Ross Fadely (NYU), Alan Heavens (Edinburgh), {\revisions and the referee}
for valuable discussion. Thomas Lumley (Auckland) also deserves credit for
ending BJB's usage of the jet colormap.
This work was funded by a Marsden Fast Start grant from the Royal Society of
New Zealand.
